Coalescent inference of mutation spectrum histories from sample frequency spectra

### 2019-08-28 manuscript/main.tex
forgot y, and no more admm I guess
adding identifiability refs

@@

Our fused LASSO \citep{tibs} loss function is then
\begin{align}
L(\boldsymbol y, \boldsymbol z) &= - \ell(\boldsymbol y, \boldsymbol z) + \lambda_\eta \left(\alpha\rho_\eta(\boldsymbol y, h, 1) + \frac{(1-\alpha)}{2}\rho_\eta(\boldsymbol y, h, 2)\right) + \lambda_\mu \left(\alpha\rho_\mu(\boldsymbol y, h, 1) + \frac{(1-\alpha)}{2}\rho_\mu(\boldsymbol y, h, 2)\right),
\end{align}
where $\lambda_\eta$ and $\lambda_\mu$ tune the regularization strength on $\eta$ and $\mu$, respectively, and $\alpha$ tunes the relative $p=1$ vs $p=2$ regularization.

@@

\section{Acknowledgements}\label{sec:ack}
Jean Feng suggested ADMM (if we end up using that).

>>>>

Some references for nonidentifiability of demographic history from the SFS: \cite{Baharian2018-np, Bhaskar2014-fu, Terhorst2015-xt, Myers2008-jp}.
It might be good to consider identifiability of mutation rate history from the SFS conditioned on demographic history.

@@

Our fused LASSO \citep{tibs} loss function is then
\begin{align}
L(\boldsymbol y, \boldsymbol z) &= - \ell(\boldsymbol y, \boldsymbol z) + \lambda_\eta \left(\alpha\rho_\eta(\boldsymbol y, h, 1) + \frac{(1-\alpha)}{2}\rho_\eta(\boldsymbol y, h, 2)\right) + \lambda_\mu \left(\alpha\rho_\mu(\boldsymbol y, \boldsymbol z, h, 1) + \frac{(1-\alpha)}{2}\rho_\mu(\boldsymbol y, \boldsymbol z, h, 2)\right),
\end{align}
where $\lambda_\eta$ and $\lambda_\mu$ tune the regularization strength on $\eta$ and $\mu$, respectively, and $\alpha$ tunes the relative $p=1$ vs $p=2$ regularization.

@@

\section{Acknowledgements}\label{sec:ack}
